Inferring Lensing Mass in the Universe \\ from Photometric Catalog Data

### 2012-10-09 doc/paper-lcr.tex
appendix B done

\section{Deriving the $\Mstar=\Mhalo$ relation}
\label{appendix:MSMH}

>>>>

\section{Inferring $\Mhalo$ given a noisy measurement of $\Mstarobs$}
\label{appendix:MSMH}

Given a noisy estimate of the stellar mass of a galaxy, $\Mstarobs$, how can
we infer the galaxy's halo mass? We seek the posterior PDF
$\Pr(\Mhalo|\Mstarobs)$, which can be expanded as follows:

\begin{eqnarray}
&& \Pr(\Mhalo|\Mstarobs) = \notag\\
&& \int d\Mstar \Pr(\Mhalo|\Mstar) \Pr(\Mstar|\Mstarobs), \notag\\
&\propto& \int d\Mstar \Pr(\Mstarobs|\Mstar) \Pr(\Mstar|\Mhalo) \Pr(\Mhalo),
\label{eq:mhalo-mstar}
\end{eqnarray}
where we have used Bayes Theorem twice to replace
$\Pr(\Mstar|\Mhalo) \Pr(\Mhalo)$ with $\Pr(\Mhalo|\Mstar) \Pr(\Mstar)$, and 
to invert $\Pr(\Mstar|\Mstarobs)$ into the sampling
distribution $\Pr(\Mstar|\Mstarobs)$, which we recognise as the likelihood
function for the observed stellar mass. Note that the ``true'' $\Mstar$ of the
galaxy is marginalised out: we are only interested in reconstructing the halo
mass. The last two terms in
\eqref{eq:mhalo-mstar} are the $\Mstar-\Mhalo$ relation from
\citet{BehrooziEtal2010}, and the halo mass function $\Pr(\Mhalo)$. We can
tabulate the product of these two from our Millenium Simulation catalog,
constructing a two-dimensional histogram of halo masses and their associated
true stellar masses (drawn from the Behroozi relation).

For each galaxy, we compute the likelihood function for its $\Mstarobs$ as a
function of the unknown $\Mstar$, and multiply it by our tabulated joint PDF.
This heavily downweights halos with $\Mstar$ values outside the observed
range. We then do the marginalisation integral by Monte Carlo, drawing
(two-dimensional) sample parameter vectors
from the downweighted histogram, discarding the $\Mstar$ values, and
constructing a one-dimensional histogram that is an estimate of
$\Pr(\Mhalo|\Mstarobs)$.
